Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-05-16 Grassmannian_cells.tex
Minor Section 2 edits

\title[Cell Decompositions for Quiver Grassmannians]{Cell Decompositions for Rank Two Quiver Grassmannians}

@@

\begin{document}
\setcounter{tocdepth}{2}

\maketitle%\tableofcontents

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Covering Theory}
\label{sec:covering}
\noindent
We refer to \cite{gab} for an introduction to covering theory.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$ and we assume in the following that all representations are finite-dimensional.

>>>>

%\title[Cell Decompositions for Quiver Grassmannians]{Cell Decompositions for Rank Two Quiver Grassmannians}

@@

\begin{document}
%\setcounter{tocdepth}{2}

%\maketitle%\tableofcontents

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Covering Theory}
\label{sec:covering}
\noindent
We refer to \cite{gab} for an introduction to covering theory.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$, and we assume in the following that all representations are finite-dimensional.
